Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-16 Scripts/Initial_Analysis.Rmd
fixed ensamble labeling problem

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
}

@@

        # possibleError_I <-  tryCatch({
        #Puts them together in one nice dataset 
        if(i == 1){
          total<- copy(cur) # <- copies the previouse data.table
        }else{ 
          setkey(total, # <- sets the data.table as "reference" ?setkey
                 index); setkey(cur,
                                index); 
          total <- merge(total, #<- Merges all the data in one single file.
                         cur,
                         all = TRUE) # <- This allows for the NA's

@@

    world_data <- world_grid %>%
      full_join(total,
                by = "index")
    # Messages
    if(inherits(possibleError, "error")){

@@

    }else{

      print(paste("Analysis done for",taxon_key, "ensamble" ,ensamble_list[c]))
    }

    if(c == 1){
      partial_ensamble <- world_data
    }else{
      spp_ensamble <- bind_rows(partial_ensamble,world_data)
    }
  }

@@

x <- dbem_import(
  taxon_key <- 600004,
  iyr <- 1951,
  fyr <- 1952,
  data_type <- "Catch",
  # ensamble_list = c(102,103),
  ensamble_list =ensamble_list,
  Path <- DBEM_path
)

@@

iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list <- seq(102,111,1)
DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
  DBEM_path <- paste(data_path,"DBEM/",sep="")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
  DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
}

@@

        # possibleError_I <-  tryCatch({
        #Puts them together in one nice dataset 
        if(i == 1){
          total<- copy(cur)  # <- copies the previouse data.table

        }else{ 
          setkey(total, # <- sets the data.table as "reference" ?setkey
                 index); setkey(cur,
                                index); 
          total <- merge(total, #<- Merges all the data in one single file.
                         cur,
                         all = TRUE)  # <- This allows for the NA's

@@

    world_data <- world_grid %>%
      full_join(total,
                by = "index")

    if(c == 1){
      partial_ensamble <- world_data

    }else{
      spp_ensamble <- bind_rows(spp_ensamble,world_data)

  # Messages
  if(inherits(possibleError, "error")){

@@

  }else{
    print(paste("Analysis done for",taxon_key, "ensamble" ,ensamble_list[c]))
  }

@@

x <- dbem_import(
  taxon_key <- 600004,
  iyr <- 1951,
  fyr <- 1952,
  data_type <- "Catch",
  ensamble_list = c(102,103,104),
  # ensamble_list =ensamble_list,
  Path <- DBEM_path
)

@@

iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list <- seq(102,111,1)
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()
